---
title: "Combine-Raro-Digitised-ATT"
output:
  pdf_document: default
  html_notebook: default
editor_options:
  chunk_output_type: console
---

```{r}

library(tidyverse)
library(sf)

root_dn = "F:/"

proj_dn = paste0(root_dn,"Rarotonga/")
ATT_dig_dn = paste0(proj_dn,"DIGITISATION/")


# Andrew's digitisation
MAT_ATT_dig_ffn = paste0(ATT_dig_dn, "AERIAL/AERIAL-ATT-OUTLINES-MAT.shp")
TUR_ATT_dig_ffn = paste0(ATT_dig_dn, "AERIAL/AERIAL-ATT-OUTLINES-TUR.shp")

# Harleys's digitisation
AVA_ATT_dig_ffn = paste0(ATT_dig_dn, "AERIAL/Harley/Avatiu_manual_mapping_30m_ATT_HB.shp")
TAK_ATT_dig_ffn = paste0(ATT_dig_dn, "AERIAL/Harley/Takuvaine_manual_mapping_30m_ATT_HB.shp")
TCA_ATT_dig_ffn = paste0(ATT_dig_dn, "AERIAL/Harley/Takitimu_manual_mapping_30m_ATT_HB.shp")

SITES = c("MAT","TUR","AVA","TAK", "TCA")
SITE_ffns = c(MAT_ATT_dig_ffn, TUR_ATT_dig_ffn, AVA_ATT_dig_ffn, TAK_ATT_dig_ffn, TCA_ATT_dig_ffn)


```


# Read the digised ATT data that Harley and I di on week of 14 May 2024

We digitised ATT in the aerial footage to extent of the Mavic 30m footage. We used Jans predictions on the Mavic Imagery to point us to where the ATT were. The 30 m imagery was resolved enough so that the deep learning could resolve the distinctive leaf pattern of ATT.

Andrew did Matavera (MAT) and Turangi (TUR), Harley did Avatiu (AVA), Takitimu (TCA) and Takuvaine (TAK).


```{r}



# i = 3


for (i in 1:length(SITE_ffns)){
  
  ATT_dig_ffn_curr = SITE_ffns[i]
  ATT_site_curr = SITES[i]
  ATT_polys_curr = st_read(ATT_dig_ffn_curr)
  
  ATT_polys_curr_hmzd = ATT_polys_curr %>% 
    mutate(
      sub_id = 1:nrow(ATT_polys_curr),
      site = ATT_site_curr,
      mapped = "NF",
      truth = "NF",
      checked = -1,
      comment = ""
    ) %>% 
    dplyr::select(
      sub_id,      site,      mapped,      truth,      checked,      comment
    )
  
  if (i == 1){
    
    ATT_polys_all_hmzd = ATT_polys_curr_hmzd
    
  } else {
    
    ATT_polys_all_hmzd = ATT_polys_all_hmzd %>% bind_rows(ATT_polys_curr_hmzd)
    
  }
  
}


ATT_polys_all_hmzd =ATT_polys_all_hmzd %>% mutate(id = 1:nrow(.))

ATT_polys_all_hmzd_fn = 'AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial.shp'
ATT_polys_all_hmzd_ffn = paste0(ATT_dig_dn, ATT_polys_all_hmzd_fn)

st_write(ATT_polys_all_hmzd, ATT_polys_all_hmzd_ffn, append = T)

```


#Following classification of the flowering using mapaccuracy save it as a new file



```{r}





ATT_polys_all_hmzd_fn = 'AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial.shp'
ATT_polys_all_hmzd_ffn = paste0(ATT_dig_dn, ATT_polys_all_hmzd_fn)

ATT_polys_all_hmzd_classfd = st_read(ATT_polys_all_hmzd_ffn) %>% 
  mutate(AREA = as.numeric(st_area(.)))

ATT_polys_all_hmzd_classfd_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro-ATT-polys-aerial_flowering_class.shp" )

st_write(ATT_polys_all_hmzd_classfd, ATT_polys_all_hmzd_classfd_ffn, append=F )


ATT_polys_all_hmzd_classfd_ng = ATT_polys_all_hmzd_classfd %>% 
  st_set_geometry(NULL) 

ATT_polys_all_hmzd_classfd_ng_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "results.csv" )
write_csv(ATT_polys_all_hmzd_classfd_ng, ATT_polys_all_hmzd_classfd_ng_ffn)

ATT_polys_all_hmzd_classfd_ng_smy1 = ATT_polys_all_hmzd_classfd_ng %>% 
  as_tibble() %>% 
  group_by(site, truth) %>% 
  summarise(
    Number_ATT = length(sub_id),
    Area_ATT = sum(AREA, na.rm)
  )


ATT_polys_all_hmzd_classfd_ng_smy1_wide = ATT_polys_all_hmzd_classfd_ng_smy1 %>% 
  select(site, truth,Number_ATT) %>% 
  spread(key = truth, value = Number_ATT) %>% 
  mutate(TOTAL = NF + NO_FLOWERS + STRONG +VERYWEAK +WEAK)


ATT_polys_all_hmzd_classfd_ng %>% filter(is.na(truth))

```

# Split big trees

Just split all the big trees. In QGIS, we filtered F:/Rarotonga/DIGITISATION/AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial_flowering_class.shp
for all trees > 20 m area

Now we need to repeat map accuracy procedure

```{r}


raro_ATT_polys_aerial_flowering_class_ffn = "F:/Rarotonga/DIGITISATION/AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial_flowering_class.shp"

ATT_POLYS = st_read(raro_ATT_polys_aerial_flowering_class_ffn)

ATT_POLYS %>% pull(site) %>%  unique()

ATT_POLYS_reset = ATT_POLYS %>% 
  mutate(
    id = 1:nrow(.),
    mapped = truth,
    truth = "UNASSIGNED",
    checked = -1) %>% 
  group_by(site) %>% 
  mutate(
    sub_id =  row_number(site))

raro_ATT_polys_aerial_flowering_class_split_ffn = "F:/Rarotonga/DIGITISATION/AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial_split_unclassed.shp"

st_write(ATT_POLYS_reset, raro_ATT_polys_aerial_flowering_class_split_ffn, append = F)






```


# and repeat analysis above -- add area and resave file
```{r}
raro_ATT_polys_aerial_split_unclassed_ffn = "F:/Rarotonga/DIGITISATION/AERIAL/Combined-Harmonised-ATT-Shapes/raro-ATT-polys-aerial_split_unclassed.shp"


raro_ATT_polys_aerial_split_unclassed = st_read(raro_ATT_polys_aerial_split_unclassed_ffn) %>% 
  mutate(AREA = as.numeric(st_area(.)),
         IS_ATT = as.integer(1))



raro_ATT_polys_aerial_split_classedflowering_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_labels.shp" )

st_write(raro_ATT_polys_aerial_split_unclassed, raro_ATT_polys_aerial_split_classedflowering_ffn, append=F )
```


# read the classed file

```{r}


raro_ATT_polys_aerial_split_classedflowering_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_polys_aerial_split_classedflowering.shp" )

ATT_POLYS = st_read(raro_ATT_polys_aerial_split_classedflowering_ffn )

ATT_POLYS_ng = ATT_POLYS %>% 
  st_set_geometry(NULL) 

ATT_POLYS_ng_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_dig_results.csv" )
write_csv(ATT_POLYS_ng, ATT_POLYS_ng_ffn)

ATT_POLYS_ng_smy1 = ATT_POLYS_ng %>% 
  as_tibble() %>% 
  group_by(site, truth) %>% 
  summarise(
    Number_ATT = length(sub_id),
    Area_ATT = sum(AREA)
  )


ATT_POLYS_ng_smy1_wide_ntrees = ATT_POLYS_ng_smy1 %>% 
  select(site, truth,Number_ATT) %>% 
  spread(key = truth, value = Number_ATT) %>% 
  mutate(
    TOTAL =  NO_FLOWERS + STRONG +VERYWEAK +WEAK,
    PERCENT_FLOWERING = 100 * (STRONG + WEAK)/TOTAL)


ATT_POLYS_ng_smy1_wide_ntrees_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_ntree_smy_results.csv" )
write_csv(ATT_POLYS_ng_smy1_wide_ntrees, ATT_POLYS_ng_smy1_wide_ntrees_ffn)



SITES = c("MAT","TUR","AVA","TAK")
EXTENT_OL_ffn = paste0("F:/Rarotonga/IMAGERY/MAVIC/EXTENTS-30m/EXTENT-", SITES,"-30m.shp")

SITE_AREAS = data.frame(SITES = SITES, AREA_SQM = NA)
for (i in 1:length(SITES)){
  # i=1
  SF = st_read(EXTENT_OL_ffn[i])
  SITE_AREAS$AREA_SQM[i] = as.numeric(st_area(SF))
  
  
  
  
}



ATT_POLYS_ng_smy1_wide_area = ATT_POLYS_ng_smy1 %>% 
  select(site, truth,Area_ATT) %>% 
  spread(key = truth, value = Area_ATT) %>% 
  left_join(SITE_AREAS, by = c("site" = "SITES")) %>% 
  mutate(
    TOTAL =  NO_FLOWERS + STRONG +VERYWEAK +WEAK,
    PERCENT_AREA_ATT_FLOWERING = 100 * (STRONG + WEAK)/TOTAL,
    PERCENT_AREA_ATT =  100*TOTAL/AREA_SQM
  )


ATT_POLYS_ng_smy1_wide_area_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_ATT_area_smy_results.csv" )
write_csv(ATT_POLYS_ng_smy1_wide_area, ATT_POLYS_ng_smy1_wide_area_ffn)



ATT_polys_all_hmzd_classfd_ng %>% filter(is.na(truth))




```


#create flowering trees only layer

```{r}


raro_ATT_polys_aerial_split_classedflowering_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_polys_aerial_split_classedflowering.shp" )

ATT_POLYS = st_read(raro_ATT_polys_aerial_split_classedflowering_ffn )

ATT_POLYS_FLOWERING_ONLY = ATT_POLYS %>% 
  filter(truth == "WEAK" | truth == "STRONG")


ATT_POLYS_FLOWERING_ONLY_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_FLOWERING_ONLY.shp" )
st_write(ATT_POLYS_FLOWERING_ONLY, ATT_POLYS_FLOWERING_ONLY_ffn, append = F )

ATT_POLYS_FLOWERING_ONLY_ffn = paste0('F:/Rarotonga/ANDREW_DEEPSEG/', "ATT_POLYS_FLOWERING_ONLY.shp" )
st_write(ATT_POLYS_FLOWERING_ONLY, ATT_POLYS_FLOWERING_ONLY_ffn, append = F )



```

# wrap in Harleys data set to the larger data set

```{r}

raro_ATT_polys_aerial_split_classedflowering_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_polys_aerial_split_classedflowering.shp" )

ATT_POLYS = st_read(raro_ATT_polys_aerial_split_classedflowering_ffn )

nrow_existing  = nrow(ATT_POLYS)

TCA_ATT_dig_ffn = paste0("F:/Rarotonga/DIGITISATION/AERIAL/Harley/Takitimu_manual_mapping_30m_ATT_HB.shp")
TCA_ATT_dig = st_read(TCA_ATT_dig_ffn)

TCA_ATT_dig_mdf = TCA_ATT_dig %>% 
  mutate(
    site="TCA",
    sub_id = 1:nrow(.),
    mapped="", 
    truth = "", 
    checked=-1, 
    comment = "",
    id = nrow_existing + sub_id,
    AREA = as.numeric(st_area(.)),
    IS_ATT=1) %>% 
  dplyr::select(sub_id, site,mapped,truth,checked,comment,id,AREA, IS_ATT,geometry)


TCA_ATT_dig_mdf_ffn ="F:/Rarotonga/DIGITISATION/AERIAL/Harley/Takitimu_manual_mapping_30m_ATT_HB_hmnzd.shp"

st_write(TCA_ATT_dig_mdf, TCA_ATT_dig_mdf_ffn, append = F)

#this will now be read by map accuracy. Classified for flowering and resaved


```

# Now after flower classification, fold this layer (Takitimu_manual_mapping_30m_ATT_HB_hmnzd.shp) into the larger data set

```{r}

TCA_ATT_dig_mdf_ffn ="F:/Rarotonga/DIGITISATION/AERIAL/Harley/Takitimu_manual_mapping_30m_ATT_HB_hmnzd.shp"
TCA_ATT_dig_mdf2 = st_read(TCA_ATT_dig_mdf_ffn)

raro_ATT_polys_aerial_split_classedflowering_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_polys_aerial_split_classedflowering.shp" )
ATT_POLYS = st_read(raro_ATT_polys_aerial_split_classedflowering_ffn )


ATT_POLYS_v2 = ATT_POLYS %>% bind_rows(TCA_ATT_dig_mdf2)
ATT_POLYS_v2_ffn =  paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "raro_ATT_polys_aerial_split_classedflowering_v2.shp" )
st_write(ATT_POLYS_v2, ATT_POLYS_v2_ffn, append = F)

library(mapview)
mapview(ATT_POLYS_v2)


```

# NOTE!!! to use a more simple name we made a copy of this file:
raro_ATT_polys_aerial_split_classedflowering_v2.shp
and called it:
ATT_POLYS_v2.shp


# finally create another version of ATT_POLYS_v2.shp and filter for only fowering trees

```{r}

ATT_POLYS_v2_ffn =paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_v2.shp" )
ATT_POLYS_v2 = st_read(ATT_POLYS_v2_ffn)

ATT_POLYS_v2_FLOWERING_ONLY = ATT_POLYS_v2 %>% 
  filter(truth == "STRONG"  | truth == "WEAK"     )

ATT_POLYS_v2_FLOWERING_ONLY_ffn = ATT_POLYS_v2_ffn =paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_v2_FLOWERING_ONLY.shp" )

st_write(ATT_POLYS_v2_FLOWERING_ONLY, ATT_POLYS_v2_FLOWERING_ONLY_ffn, append = F)




```



# Repeat the stats on version 2 of the data

```{r}


ATT_POLYS_v2_ffn =paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_v2.shp" )
ATT_POLYS_v2 = st_read(ATT_POLYS_v2_ffn)


ATT_POLYS_ng = ATT_POLYS_v2 %>% 
  st_set_geometry(NULL) 

ATT_POLYS_ng_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_dig_results.csv" )
write_csv(ATT_POLYS_ng, ATT_POLYS_ng_ffn)

ATT_POLYS_ng_smy1 = ATT_POLYS_ng %>% 
  as_tibble() %>% 
  group_by(site, truth) %>% 
  summarise(
    Number_ATT = length(sub_id),
    Area_ATT = sum(AREA)
  )


ATT_POLYS_ng_smy1_wide_ntrees = ATT_POLYS_ng_smy1 %>% 
  select(site, truth,Number_ATT) %>% 
  spread(key = truth, value = Number_ATT) %>% 
  mutate(
    TOTAL =  NO_FLOWERS + STRONG +VERYWEAK +WEAK,
    PERCENT_FLOWERING = 100 * (STRONG + WEAK)/TOTAL)


ATT_POLYS_ng_smy1_wide_ntrees_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_ntree_smy_results.csv" )
write_csv(ATT_POLYS_ng_smy1_wide_ntrees, ATT_POLYS_ng_smy1_wide_ntrees_ffn)



SITES = c("MAT","TUR","AVA","TAK")
EXTENT_OL_ffn = paste0("F:/Rarotonga/IMAGERY/MAVIC/EXTENTS-30m/EXTENT-", SITES,"-30m.shp")

SITE_AREAS = data.frame(SITES = SITES, AREA_SQM = NA)
for (i in 1:length(SITES)){
  # i=1
  SF = st_read(EXTENT_OL_ffn[i])
  SITE_AREAS$AREA_SQM[i] = as.numeric(st_area(SF))
  
  
  
  
}



ATT_POLYS_ng_smy1_wide_area = ATT_POLYS_ng_smy1 %>% 
  select(site, truth,Area_ATT) %>% 
  spread(key = truth, value = Area_ATT) %>% 
  left_join(SITE_AREAS, by = c("site" = "SITES")) %>% 
  mutate(
    TOTAL =  NO_FLOWERS + STRONG +VERYWEAK +WEAK,
    PERCENT_AREA_ATT_FLOWERING = 100 * (STRONG + WEAK)/TOTAL,
    PERCENT_AREA_ATT =  100*TOTAL/AREA_SQM
  )


ATT_POLYS_ng_smy1_wide_area_ffn = paste0(ATT_dig_dn,'AERIAL/Combined-Harmonised-ATT-Shapes/', "ATT_POLYS_ATT_area_smy_results.csv" )
write_csv(ATT_POLYS_ng_smy1_wide_area, ATT_POLYS_ng_smy1_wide_area_ffn)



ATT_polys_all_hmzd_classfd_ng %>% filter(is.na(truth))




```



#combine all the outline files

```{r}


SITES = c("MAT","TUR","AVA","TAK", "TCA")
EXTENT_OL_ffn = paste0("F:/Rarotonga/IMAGERY/MAVIC/EXTENTS-30m/EXTENT-", SITES,"-30m.shp")

for (isite in 1:length(SITES)){
  
  csite = st_read(EXTENT_OL_ffn[isite])
  
  if (isite == 1){
    
    training_areas_mavic_30m = csite
    
    
  } else {
    
    training_areas_mavic_30m = training_areas_mavic_30m %>% bind_rows(csite)
    
  }
  
  
  
  
}

training_areas_mavic_30m_ffn = paste0("F:/Rarotonga/IMAGERY/MAVIC/EXTENTS-30m/EXTENT-ALLSITES-30m.shp")
st_write(training_areas_mavic_30m, training_areas_mavic_30m_ffn, append = F)


```

# Ok Jan has run deep learning on ATT_POLYS_v2.shp
The file is called: raro_aerial_prediction_jan_first_try.gpkg

We created a rectangles throughout the island and intersected these with Jans layerto create a new layer called 
new-training-areas_x_raro_first_attempt.shp

```{r}

# The predictions are in 
polys_pred_select_ffn = "F:/Rarotonga/ANDREW_DEEPSEG/New-Training-Areas/new-training-areas_x_raro_first_attempt.shp"
polys_pred_select = st_read(polys_pred_select_ffn)

polys_pred_select_mdf = polys_pred_select %>% 
  mutate(
    id = 1:nrow(.),
    mapped = "ATT-F",
    truth = "",
    checked = as.integer(-1),
    comment = "",
    AREA = as.numeric(st_area(.))) %>% 
  filter(AREA > 5)

polys_pred_select_mdf_ffn = "F:/Rarotonga/ANDREW_DEEPSEG/New-Training-Areas/new-training-areas_x_raro_first_attempt_mapacc.shp"
st_write(polys_pred_select_mdf, polys_pred_select_mdf_ffn, append = F)

#mapaccuracy -v F:/Rarotonga/ANDREW_DEEPSEG/New-Training-Areas/new-training-areas_x_raro_first_attempt.shp F:\Rarotonga\IMAGERY\AERIAL\raro-ortho-v3.kea






```


#Resume this work on 4/6/24

```{r}




# The predictions are in 
polys_pred_select_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Jan-Pred-in-TA-Round3-Sel.shp"
file.exists(polys_pred_select_ffn)
polys_pred_select = st_read(polys_pred_select_ffn)

polys_pred_select_mdf = polys_pred_select %>% 
  mutate(
    id = 1:nrow(.),
    mapped = "ATT-F",
    truth = "",
    checked = as.integer(-1),
    comment = "",
    AREA = as.numeric(st_area(.))) %>% 
  filter(AREA > 5)

polys_pred_select_mdf_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Jan-Pred-in-TA-Round3-Sel_4_mapacc.shp"
st_write(polys_pred_select_mdf, polys_pred_select_mdf_ffn, append = F)

```


# AFTER GOING THROUGH THIS LAYER IN MAP ACCURACY AND DOING SOME TIDYING IN qgis

```{r}

#Read the Map accuracy veriufied file.

round3_training_polys_all_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Jan-Pred-in-TA-Round3-Sel_4_mapacc.shp"
round3_training_polys_all = st_read(round3_training_polys_all_ffn) # 704 features

#filter this data set for those polygons that are strongly flowering ("_FSO")
round3_training_polys_FSO = round3_training_polys_all %>% 
  filter(truth == "STRONG") %>% 
  mutate(IS_ATT = as.integer(1)) # 46 features


len_na_fid = length(which(is.na(round3_training_polys_FSO$fid)))

if (len_na_fid > 0){
  
  max_fid = max(round3_training_polys_FSO$fid, na.rm=T)
  fids_fill = (max_fid+1):(max_fid+len_na_fid)
  round3_training_polys_FSO$fid[which(is.na(round3_training_polys_FSO$fid))] = fids_fill
  round3_training_polys_FSO$fid = as.integer(round3_training_polys_FSO$fid)
  
}

len_na_fid_revised = length(which(is.na(round3_training_polys_FSO$fid)))




round3_training_polys_FSO_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Jan-Pred-in-TA-Round3-Sel_4_mapacc_FSO.shp"
st_write(round3_training_polys_FSO, round3_training_polys_FSO_ffn, append = F)

#filter this data set for those polygons that are strongly or weakly flowering ("_FSW")
round3_training_polys_FSW = round3_training_polys_all %>%
  filter(truth == "STRONG" | truth == "WEAK") %>% 
  mutate(IS_ATT = as.integer(1))   # 170 features

len_na_fid = length(which(is.na(round3_training_polys_FSW$fid)))

if (len_na_fid > 0){
  
  max_fid = max(round3_training_polys_FSW$fid, na.rm=T)
  fids_fill = (max_fid+1):(max_fid+len_na_fid)
  round3_training_polys_FSW$fid[which(is.na(round3_training_polys_FSW$fid))] = fids_fill
  round3_training_polys_FSW$fid = as.integer(round3_training_polys_FSW$fid)
  round3_training_polys_FSW = round3_training_polys_FSW %>% dplyr::select(-fid)
}

len_na_fid_revised = length(which(is.na(round3_training_polys_FSW$fid)))


round3_training_polys_FSW_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Jan-Pred-in-TA-Round3-Sel_4_mapacc_FSW.shp"
st_write(round3_training_polys_FSW, round3_training_polys_FSW_ffn, append = F)






round3_training_areas_ffn = "F:/Rarotonga/Deep-Learning-Progress/Training-Areas-Round3/Training-Areas-Round3-Selected.shp"
round3_training_areas = st_read(round3_training_areas_ffn)

library(mapview)
options(viewer=NULL)
mapview(round3_training_areas)




```


# Now combine the falcateria layers that Harley has made -->


```{r}


dig_folder = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/Deep-Learning-Progress/Aerial-digitisation/Harley/"

fls = list.files(dig_folder, pattern = "Falcataria\\_HB\\.shp$")

sitenames = str_extract(fls, "^\\w{1,20}(?=_manual_mapping_30m_Falcataria_HB\\.shp)")

len_good=0

for (isite in 1:length(sitenames)){
  
  
  
  # isite=1
  csite = sitenames[isite]
  fname = paste0(csite, "_manual_mapping_30m_Falcataria_HB.shp")
  ffname = paste0(dig_folder, fname)
  
  file.exists(ffname)
  
  falc_polys_curr = st_read(ffname) %>% 
    mutate(
      AREA_SQM = as.numeric(st_area(.)),
      site = csite,
      IS_FALC = as.integer(1)) 
  
  nrow_c_file = nrow(falc_polys_curr)
  
  if (nrow_c_file > 0){
    len_good = len_good + 1
    if (len_good==1){
      
      combined_falc_polys = falc_polys_curr
    }else{
      
      combined_falc_polys = bind_rows(combined_falc_polys, falc_polys_curr)
    }
    
    
    
  }
  
  
  
}


combined_falc_polys_ffn = paste0(dig_folder, "all_sites_combined_manual_mapping_30m_Falcataria_HB_combined.shp")
st_write(combined_falc_polys, combined_falc_polys_ffn, append = F)



```



