
---
title: "raro-MainLine"
output: html_notebook
editor_options: 
  chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
chunk_output_type: console
---



# Libraries and folders
# Settings, palletes, orders and include-lists

```{r}

library(raster)
library(exactextractr)
library(fasterize)
library(hsdar)

options(show_col_types = FALSE)
options(readr.show_col_types = FALSE)


proj_dn = "PRJ3606-MFAT-MISCCAP/"


# identify the computer (and OS)
Current_PC <- Sys.info()["nodename"]

if (Current_PC == "EANZ-DT01-Linux") {
  root = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Projects/",proj_dn)
  ncore_rec = 15
} else if (Current_PC == "EANZ-DT01") {
  root = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Projects/", proj_dn)
  ncore_rec = 15
  
} else if (Current_PC == "styx") {
  root = paste0("/mnt/data/mcmillana/",proj_dn)
  ncore_rec = 64
} else if (Current_PC == "L-8P30JW3") {
  root = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Projects/", proj_dn)
  ncore_rec = 18
} else if (Current_PC == "PN-VIVE-W10") {
  root = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Projects/", proj_dn)
  ncore_rec = 15
} else {
  root = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Projects/", proj_dn)
  ncore_rec = 15
}






datadir = paste0(root, "data/")
plotdir = paste0(root, "plots/")
tabledir = paste0(root, "tables/")

root2 = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/"
datadir2 = paste0(root2,"Data/")

planetdir2 = paste0(datadir2, "Rarotonga/PlanetData/original_delivery/")

align_dn = paste0(datadir2, "Rarotonga/Aligned-Data/")


# there are 5 planet products

# 1. analytics_udm2
# 2. panchromatic
# 3. pansharpened_udm2
# 4. analytic_sr_udm2
# 5. visual

#there are 4 different dates

# 1. 19 July 2023
# 2. 24 July 2023
# 3. 7 Aug 2023
# 4. 8 Aug 2023




A = system('gdalinfo')













util_script = paste0("C:/Users/McMillanAn/OneDrive - MWLR/Code/R/utils/", "mcm_sp_utils.R")
source(util_script)


hahs_script = paste0("D:/HAHS_Projects/code/R/HAHS_Processing/", "HAHS_utils.R")
source(hahs_script)



cbbPalette <- c("#D55E00", "#56B4E9", "#CC79A7", "#009E73", "#000000", "#E69F00", "#56B4E9")

Palette_01 <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

Palette_02 <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2","#000000", "#CC79A7")




```

The belo chunk can only be run on my laptop (not on VIVE)

```{r}

system('wsl cd ~/raroor')
system('wsl ls ~/rarobasic')


# fn_ptrn = "20230808_190708_ssc16d1_0006_basic_analytic.tif"

rarobasic_dn = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/PlanetData/basic_scenes/Rarotonga_Scenes_skysatscene_basic_analytic_udm2/SkySatScene/"

dir.exists(rarobasic_dn)

fn_ptrn = "\\d{8}\\_\\d{6}\\_ssc\\d{2}d\\d{1}\\_\\d{4}_basic_analytic.tif"

flist_basic_an = list.files(rarobasic_dn, pattern = fn_ptrn)
flist_basic_an


#Sample gdal command for wsl
SCMD = "wsl gdalwarp -t_srs epsg:32704 -wo SAMPLE_GRID=NO -et 0 -rpc -srcnodata 0 -dstnodata 'None' -to RPC=/home/mcmillanan/rarobasic/ortho/Raro_Mesh_DSM_2023.tif /home/mcmillanan/rarobasic/20230808_190708_ssc16d1_0015_basic_analytic.tif /home/mcmillanan/rarobasic/ortho/20230808_190708_ssc16d1_0015_basic_analytic_ortho3.tif"

system(SCMD) # cannot find gdalinfo



sep = "\\\\"
rarobasic_dn_4cmd = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/PlanetData/basic_scenes/Rarotonga_Scenes_skysatscene_basic_analytic_udm2/SkySatScene/"


# 
# 
# CMD = paste0("gdalinfo ", "\"",  rarobasic_dn_4cmd, "\"", "20230808_193818_ssc15d3_0012_basic_analytic.tif")
# print(CMD)
# system(CMD)

W10CMD_stub1 = "gdalwarp -t_srs epsg:32704 -wo SAMPLE_GRID=NO -et 0 -rpc -srcnodata 0 -dstnodata 'None' -to RPC="

# DSM_ffname = paste0("\"",  rarobasic_dn_4cmd, "/ortho/Raro_Mesh_DSM_2023.tif", "\"")
# basic_strip_ffname = paste0("\"",  rarobasic_dn_4cmd, "20230808_193818_ssc15d3_0012_basic_analytic.tif", "\"")
# basic_strip_ortho_ffname = paste0("\"",  rarobasic_dn_4cmd, "/ortho/20230808_193818_ssc15d3_0012_basic_analytic_ortho.tif", "\"")

qm = "\""
```


Loop through all images with pattern: 20230808_190708_ssc16d3_0015_basic_analytic.tif and orthorectify using RPC
(following approach in https://up42.com/blog/how-to-perform-orthorectification-a-practical-guide#practical-example)

```{r}

for (ifile in 1:length(flist_basic_an)){
  
  # ifile = 1
  basic_strip_ffname_curr = paste0(qm,rarobasic_dn_4cmd, flist_basic_an[ifile], qm)
  basic_strip_ffname_ortho_curr = paste0(qm, rarobasic_dn_4cmd, "ortho/", tools::file_path_sans_ext(flist_basic_an[ifile]),"_ortho.tif", qm)
  
  CMD = paste0(W10CMD_stub1, DSM_ffname, " ", basic_strip_ffname_curr, " ", basic_strip_ffname_ortho_curr)
  print(CMD)
  system(CMD)
}


CMD = paste0(W10CMD_stub1, DSM_ffname, " ", basic_strip_ffname, " ", basic_strip_ortho_ffname)
print(CMD)
system(CMD)


```

Run some gdal commands to merge these tifs together

```{r}

# 1. Create a vrt

gdalbuildvrt nelson-tasman-2021-DEM.vrt *.kea



# 2. Create a kea from the VRT
gdal_translate -of KEA nelson-tasman-2021-DEM.vrt ../nelson-tasman-2021-DEM.kea


# 3. add overviews to the KEA

gdaladdo -r average LCLU.kea

```


# Extract the satellite imagery through the Mavic Extents


```{r}


# get a  list of all the relevant planet files
planetdir2_sr = paste0(planetdir2, "Rarotonga_July_Aug_2023_skysatcollect_analytic_sr_udm2 (1)/SkySatCollect/")

PTRN = "\\d{8}\\_\\d{6}\\_ssc\\d{1,3}\\_u\\d{4}\\_analytic_SR.tif$"

dir.exists(planetdir2_sr)
list.files(planetdir2_sr) 

planet_sr_flist = list.files(planetdir2_sr, pattern = PTRN, full.names = T) 

planet_SR_NUM = paste0("SR0", 1:7)
planet_sr_dates = str_extract(basename(planet_sr_flist), "^\\d{8}")
planet_ssc_nos = str_extract(basename(planet_sr_flist), "ssc\\d{1,3}")
planet_u_nos = str_extract(basename(planet_sr_flist), "u\\d{4}")
planet_img_UID = paste0(planet_SR_NUM,"_",planet_sr_dates, "_", planet_ssc_nos,"_", planet_u_nos)

# get a list of the shape files that are the extents of tthe 100 m Mavic flights

Mavic_extents_dn = align_dn 
Mavic_extents_ffns = list.files(Mavic_extents_dn, pattern = "MAVIC-RGB-\\w{3}-\\d{6}-100M-POLYEXT-N\\d{5}-V\\d{2}.gpkg", full.names = T)

for (iimg in 1:length(planet_sr_flist)){
  
  # iimg=1
  cimg = rast(planet_sr_flist[iimg])
  cimg_UID = planet_img_UID[iimg]
  
  for (ipoly in 1:length(Mavic_extents_ffns)){
    
    # ipoly = 1
    cpoly = st_read(Mavic_extents_ffns[ipoly])
    
    
    cpoly_ext = ext(cpoly)
    cimg_ext = ext(cimg)
    
    IX = intersect(cpoly_ext, cimg_ext)
    
    if(!is.null(IX)){
      
      extract = crop(cimg, cpoly)
      
      extract_fn = paste0(cimg_UID,"_clip_", substr(cpoly$location,8,10), ".tif")
      extract_ffn = paste0(align_dn,extract_fn )
      
      writeRaster(extract, extract_ffn, overwrite=T)
    }
  }
  
  
  
  
  
}
#


```


# CHUNK 5001. create polygon tiles of HAHS data

```{r}




tile_dn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/"

create_tile_polygons(tile_dn)



```

# CHUNK 5002. create polygon tiles of HAHS data

```{r}




tile_dn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/"

create_tile_polygons(tile_dn)



```

Blue 450-515 nm Green 515-595 nm Red 605-695 nm NIR 740-900 nm PAN 450-900 nm




# ===================================
# SECTION 6000 - HSI ANALYSIS
# ===================================

# CHNK 6001. create polygon tiles of HAHS data

```{r}

# > align_dn
# [1] "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/Aligned-Data/"


POLYLBLS_N00005_ffn = paste0(align_dn, "MAVIC-RGB-TUR-230811-100M-POLYLBLS-N00005-V01.gpkg.shp") 
POLYLBLS_N00005 = st_read(POLYLBLS_N00005_ffn)

POLYLBLS_N00005_nogeo = POLYLBLS_N00005 %>% st_set_geometry(NULL)
POLYLBLS_N00005_nogeo_ffn = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/Polygon-CSV-Files/ MAVIC-RGB-TUR-230811-100M-POLYLBLS-N00005-V01.csv"
write_csv(POLYLBLS_N00005_nogeo, POLYLBLS_N00005_nogeo_ffn)

# mapview(POLYLBLS_N00005)


# Create a layer of pure ATT with Confidence Level 5

POLYLBLS_N00005_ATT_Only_Q5 = POLYLBLS_N00005 %>% 
  filter(SPS == "ATT" & CONFIDENCE==5)

POLYLBLS_N00005_ATT_Only_Q5_ffn = paste0(align_dn, "POLYLBLS_N00005_ATT_Only_Q5.gpkg")
st_write(POLYLBLS_N00005_ATT_Only_Q5, POLYLBLS_N00005_ATT_Only_Q5_ffn, append = F)


# Intersect the pure ATT polygon layers with the HS Tiles Polygon Layer

HS_TILE_POLYS_BOUNDARY = st_read("F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/TILE_POLYGONS.shp")  %>%
  st_combine()

mapview(HS_TILE_POLYS_BOUNDARY)


POLYLBLS_N00005_ATT_Only_Q5_ffn = paste0(align_dn, "POLYLBLS_N00005_ATT_Only_Q5.gpkg")
POLYLBLS_N00005_ATT_Only_Q5 = st_read(POLYLBLS_N00005_ATT_Only_Q5_ffn)

RASTOL_NANO_TUR_N00006_ffn = paste0(align_dn, "M600-NANO-TUR-230811-80M-RASTOL-N00006-V01.shp")
RASTOL_NANO_TUR_N00006 = st_read(RASTOL_NANO_TUR_N00006_ffn)

POLYLBLS_N00005_ATT_Only_Q5_HS = st_intersection(POLYLBLS_N00005_ATT_Only_Q5, RASTOL_NANO_TUR_N00006)
POLYLBLS_N00005_ATT_Only_Q5_HS_ffn = paste0(align_dn, "POLYLBLS_N00005_ATT_Only_Q5_HS.gpkg")
st_write(POLYLBLS_N00005_ATT_Only_Q5_HS, POLYLBLS_N00005_ATT_Only_Q5_HS_ffn, append = F)


mapview(POLYLBLS_N00005_ATT_Only_Q5_HS)


```


# CHNK 6002. Extract Hyperspectral Data through Polygons 


```{r}

POLY_fn = "M600-NANO-TUR-230811-80M-POLYLBL-N00007-V01.shp"
POLY_ffn = paste0(align_dn, POLY_fn)
POLY = st_read(POLY_ffn)

r_TUR_HS_80m_ffn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_32704.kea"
r_TUR_HS_80m = rast(r_TUR_HS_80m_ffn)


r_TUR_HS_80m_ffn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE.kea"
r_TUR_HS_80m = rast(r_TUR_HS_80m_ffn)

# crop and mask

r_ffn = r_TUR_HS_80m_ffn
v_ffn = POLY_ffn
id_tag = "id"

fname_list = clip_r2v(r_ffn, v_ffn, id_tag)

#grab the id
r_num = as.numeric(str_extract(fname_list, pattern = "(?<=EXTR\\_)\\d{5}"))
r_clip_id = as.numeric(str_extract(fname_list, pattern = "(?<=id\\_tag\\_)\\d{5}"))


```

# CHNK 6003. Start plotting data from extracts

```{r}

# r_clip_ffn = ("F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_EXTR/multi_or_TUR_20230811_2BYTE_EXTR_00019_id_tag_00012.tif")
# 
# 
# 
# r_clip_ffn = ("F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_EXTR/multi_or_TUR_20230811_2BYTE_EXTR_00019_id_tag_00012.tif")



clip_dn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_EXTR"
clip_fls = list.files(clip_dn, pattern = "tif$",full.names = T,include.dirs = F)

#get the bandnumbers and the wavelengths
bnwl = get_bnwl()
bnames_lng = paste0("b", formatC(bnwl$bn, width = 5, flag = "0"), "-", formatC(bnwl$wl, digits = 5))
bnames = paste0("b", formatC(bnwl$bn, width = 3, flag = "0"))

#read the shape file again to get the metadata
POLY_fn = "M600-NANO-TUR-230811-80M-POLYLBL-N00007-V01.shp"
POLY_ffn = paste0(align_dn, POLY_fn)
POLY = st_read(POLY_ffn)
print(r_clip_id)
ALL_POLY_ATTR = POLY %>% st_set_geometry(NULL) 

for (ifile in 1:length(clip_fls)){
  
  # ifile = 1
  
  
  
  cclip_ffn = clip_fls[ifile]
  
  print(paste("Processing", cclip_ffn))
  
  #grab the id
  r_clip_id = as.numeric(str_extract(cclip_ffn, pattern = "(?<=id\\_tag\\_)\\d{5}"))
  
  #grab the id
  # r_clip_id = as.numeric(str_extract(cclip_ffn, pattern = "(?<=id\\_tag\\_)\\d{5}"))
  
  r_clip = rast(cclip_ffn)
  # plot(r_clip)
  
  rval_DN = values(r_clip, dataframe=T, na.rm = T) %>% as_tibble()
  rval = rval_DN/1e4
  
  
  names(rval) <- bnames
  
  stat_list = list(
    # npix = ~length(.x),
    mean = ~mean(.x, na.rm = T),
    sd = ~sd(.x, na.rm = T),
    min = ~min(.x, na.rm = T),
    max = ~max(.x, na.rm = T),
    median = ~median(.x, na.rm = T)
  )
  
  stat_chvec = c("mean", "sd", "min", "max", "median")
  
  
  for (istat in 1:length(stat_list)){
    # istat=1
    cstat = stat_chvec[istat]
    
    rval_stats = rval %>% 
      summarise(
        across(everything(), stat_list[[cstat]])
      ) 
    rval_stats_tr = t(rval_stats) %>% as.data.frame() %>% as_tibble()
    names(rval_stats_tr) = cstat
    if (istat==1){
      POLY_STATS = bind_cols(bnwl, rval_stats_tr)
    }else{
      
      POLY_STATS = bind_cols(POLY_STATS, rval_stats_tr)
    }
    
  }
  
  
  #grab the meta data specific to this polygon
  POLY_ATTR = ALL_POLY_ATTR %>% filter(id == r_clip_id) %>% slice(1)
  
  TXTLINE_1 = paste0("id         = ", POLY_ATTR$id)
  TXTLINE_2 = paste0("species    = ", POLY_ATTR$SPS)
  TXTLINE_3 = paste0("Confidence = ", POLY_ATTR$CONFIDENCE)
  
  #collate the data
  POLY_STATS_WLBL = POLY_STATS %>% mutate(id = POLY_ATTR$id)
  
  if (ifile == 1){
    POLY_STATS_COLL = POLY_STATS_WLBL
  }else{
    POLY_STATS_COLL = bind_rows(POLY_STATS_COLL, POLY_STATS_WLBL)
  }
  
  #plot the spectra from a single polygon
  
  g = ggplot(POLY_STATS) + geom_ribbon(aes(x = wl, ymin = mean-sd, ymax = mean+sd), fill = "pink")
  g = g + geom_line(aes(x = wl, y = mean), color = "dark blue")
  g = g + labs(x = "Wavelength (nm)", y = "reflectance")
  g = g + lims(x = c(380,1000), y = c(-.05,.8))
  g = g + annotate("text", x = 450, y = .6, label = TXTLINE_1,)
  g = g + annotate("text", x = 450, y = .55, label = TXTLINE_2)
  g = g + annotate("text", x = 450, y = .5, label = TXTLINE_3)
  
  fig_fn = paste0(strip_fn(cclip_ffn),".png")
  fig_dn = paste0(clip_dn, "/", "cclip_spectra/" )
  if (!dir.exists(fig_dn)){dir.create(fig_dn, recursive = T, showWarnings = F)}
  fig_ffn=paste0(fig_dn, fig_fn)
  
  ggsave(fig_ffn, g)
  
  
  #save the collated data
  POLY_STATS_COLL_dn = paste0(clip_dn, "/", "cclip_data/" )
  if (!dir.exists(POLY_STATS_COLL_dn)){dir.create(POLY_STATS_COLL_dn, recursive = T, showWarnings = F)}
  POLY_STATS_COLL_fn = "POLY_STATS_COLL.RDS"
  POLY_STATS_COLL_ffn = paste0(POLY_STATS_COLL_dn, POLY_STATS_COLL_fn)
  saveRDS(POLY_STATS_COLL, POLY_STATS_COLL_ffn)
  
}




```

# CHNK 6004. Analyse the collated HS data

```{r}


clip_dn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_EXTR"

POLY_STATS_COLL_dn = paste0(clip_dn, "/", "cclip_data/" )
POLY_STATS_COLL_fn = "POLY_STATS_COLL.RDS"
POLY_STATS_COLL_ffn = paste0(POLY_STATS_COLL_dn, POLY_STATS_COLL_fn)

POLY_STATS_COLL = readRDS(POLY_STATS_COLL_ffn)

#read the shape file again to get the metadata
POLY_fn = "M600-NANO-TUR-230811-80M-POLYLBL-N00007-V01.shp"
POLY_ffn = paste0(align_dn, POLY_fn)
POLY = st_read(POLY_ffn)
print(r_clip_id)
ALL_POLY_ATTR = POLY %>% st_set_geometry(NULL) 

#add the metadata to the collated data set
POLY_STATS_COLL_WMETA = POLY_STATS_COLL %>% 
  left_join(ALL_POLY_ATTR, by = "id") %>% 
  mutate(SPS2 = case_when(
    SPS == "ATT" ~ "ATT", 
    SPS == "FALC" ~ "FALC",
    SPS != "ATT" & SPS != "FALC" ~"OTHER"
  ))




```


# ~~~~~~~~~~~~~~~~ #
# Figure 6001 - Plot all mean spectra coloring by species
# ~~~~~~~~~~~~~~~~ #


```{r}

fignum = 6001
figdesc = "mean-spectra-colored-by-species"
figfmt = "png"
fig_ffn = paste0(plotdir, fignum,"-", figdesc, ".", figfmt)


POLY_STATS_COLL_WMETA_grp = POLY_STATS_COLL_WMETA %>% filter(SPS2 != "OTHER")

g = ggplot(POLY_STATS_COLL_WMETA_grp) 
# g = g + geom_ribbon(aes(x = wl, ymin = mean-sd, ymax = mean+sd, fill = SPS2, alpha = 0.5))
g = g + geom_line(aes(wl, mean, group = id,color = SPS2))
g

# g=g + scale_color_manual(name = "Land Cover")
g = g + labs(x = "wavelength (nm)" , y = "Reflectance")
g = gab_style(g,1)

g = g +guides(color=guide_legend(nrow=2,byrow=TRUE))
# g = g + theme
g


WD = 28
HT = 8/18*28

specdim = F


ggsave(filename = fig_ffn, plot = g, width = WD, height = HT, units = "cm", bg = "white")

if (specdim){
  ggsave(filename = fig_ffn, plot = g, width = WD, height = HT, units = "cm", bg = "white")
} else {
  ggsave(filename = fig_ffn, plot = g,  units = "cm", bg = "white")
}


```


# ~~~~~~~~~~~~~~~~ #
# Figure 6002 - Plot mean of mean spectra coloring by species
# ~~~~~~~~~~~~~~~~ #


```{r}

fignum = 6002
figdesc = "mean-of-mean-spectra-colored-by-species"
figfmt = "png"
fig_ffn = paste0(plotdir, fignum,"-", figdesc, ".", figfmt)


POLY_STATS_COLL_WMETA_sts = POLY_STATS_COLL_WMETA %>% 
  group_by(SPS2, bn) %>% 
  summarise(wl = first(wl),
            refl_mean = median(median),
            refl_sd = sqrt(mean(sd^2))) %>% 
  filter(SPS2 != "OTHER")

g = ggplot(POLY_STATS_COLL_WMETA_sts) 
g = g + geom_ribbon(aes(x = wl, ymin = refl_mean-refl_sd, ymax = refl_mean+refl_sd, fill = SPS2), alpha = .25)
g = g + geom_line(aes(wl, refl_mean, color = SPS2), size = 1)
g

# g=g + scale_color_manual(name = "Land Cover")
g = g + labs(x = "wavelength (nm)" , y = "Reflectance")
g = gab_style(g,1)

g = g +guides(color=guide_legend(nrow=2,byrow=TRUE))
# g = g + theme
g


WD = 28
HT = .75*WD

specdim = F



if (specdim){
  ggsave(filename = fig_ffn, plot = g, width = WD, height = HT, units = "cm", bg = "white")
} else {
  ggsave(filename = fig_ffn, plot = g,  units = "cm", bg = "white")
}


```

# CHNK 6005. Hyperspectral End members

```{r}

r_TUR_HS_80m_ffn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE.kea"
r_TUR_HS_80m = rast(r_TUR_HS_80m_ffn)

POLYLBLHSEM_ffn = paste0(align_dn, "M600-NANO-TUR-230811-80M-POLYLBLHSEM-N00008-V01.shp")
# crop and mask

r_ffn = r_TUR_HS_80m_ffn
v_ffn = POLYLBLHSEM_ffn
id_tag = "id"
extract_tag = "POLYLBLHSEM-N00008"

fname_list = clip_r2v(r_ffn, v_ffn, id_tag, extract_tag = extract_tag,makeplots = T, collatedata = T)

#now grab the collated data

extract_dn = paste0(dirname(r_TUR_HS_80m_ffn), "/", strip_fn(r_TUR_HS_80m_ffn), "_EXTR_" , extract_tag, "/")
colldata_dn = paste0(extract_dn, "cclip_data/")
colldata_ffn = paste0(colldata_dn, "POLY_STATS_COLL.RDS")

colldata = readRDS(colldata_ffn)
colldata_FL = colldata %>% filter(class=="ATT-FL")

```


# ~~~~~~~~~~~~~~~~ #
# Figure 6003 - Plot mean of end members
# ~~~~~~~~~~~~~~~~ #


```{r}

fignum = 6003
figdesc = "mean-of-mean-spectra-end-members"
figfmt = "png"
fig_ffn = paste0(plotdir, fignum,"-", figdesc, ".", figfmt)

facet_or_single = "single"

colldata_sts = colldata %>% 
  group_by(class, bn) %>% 
  summarise(wl = first(wl),
            refl_mean = median(median, na.rm = T),
            refl_sd = sqrt(mean(sd^2))) %>% 
  mutate(
    target = case_when(
      class == "ATT-BF" ~ "ATT - well-lit leaves",
      class == "ATT-FL" ~ "ATT - flowers",
      class == "FALC-BF" ~ "Falcateria - well-lit leaves",
      class == "SPS12-BF" ~ "Species#12 - well-lit leaves",
    )
  )

g = ggplot(colldata_sts) 

if (facet_or_single=="facet"){
  g = g + geom_ribbon(aes(x = wl, ymin = refl_mean-refl_sd, ymax = refl_mean+refl_sd), alpha = .25)
  g = g + facet_wrap(~target)
  g = g + geom_line(aes(wl, refl_mean), size = 1)
} else {
  
  # g = g + geom_ribbon(aes(x = wl, ymin = refl_mean-refl_sd, ymax = refl_mean+refl_sd, fill = target), alpha = .25)
  
  g = g + geom_line(aes(wl, refl_mean, color= target), size = 1)
  
}
g

# g=g + scale_color_manual(name = "Land Cover")
g = g + labs(x = "wavelength (nm)" , y = "Reflectance")
g = gab_style(g,1)

g = g +guides(color=guide_legend(nrow=2,byrow=TRUE))

g = g + theme(
  legend.text = element_text(size = 10),
  legend.title =  element_blank())
g


WD = 28
HT = .75*WD

specdim = F



if (specdim){
  ggsave(filename = fig_ffn, plot = g, width = WD, height = HT, units = "cm", bg = "white")
} else {
  ggsave(filename = fig_ffn, plot = g,  units = "cm", bg = "white")
}


```



# CHNK 6006. Specify Planet Data and MAVIC bands


```{r}

# https://ag.dji.com/mavic-3-m/specs
MAVIC_MS_B1_G_spec_centre = 560
MAVIC_MS_B2_R_spec_centre = 650
MAVIC_MS_B3_RE_spec_centre = 730
MAVIC_MS_B4_NIR_spec_centre = 860

MAVIC_MS_B1_G_spec_width = 16
MAVIC_MS_B2_R_spec_width = 16
MAVIC_MS_B3_RE_spec_width = 16
MAVIC_MS_B4_NIR_spec_width = 26

MAVIC_MS_spec_centres = c(MAVIC_MS_B1_G_spec_centre, MAVIC_MS_B2_R_spec_centre, MAVIC_MS_B3_RE_spec_centre, MAVIC_MS_B4_NIR_spec_centre) 

MAVIC_MS_spec_widths = c(MAVIC_MS_B1_G_spec_width, MAVIC_MS_B2_R_spec_width, MAVIC_MS_B3_RE_spec_width, MAVIC_MS_B4_NIR_spec_width) 

MAVIC_MS_spec = data.frame(centre = MAVIC_MS_spec_centres, width = MAVIC_MS_spec_widths)



SKYSAT_MS_B1_B_spec_centre = 483
SKYSAT_MS_B2_R_spec_centre = 555
SKYSAT_MS_B3_RE_spec_centre = 650
SKYSAT_MS_B4_NIR_spec_centre = 820

SKYSAT_MS_B1_G_spec_width = 65
SKYSAT_MS_B2_R_spec_width = 80
SKYSAT_MS_B3_RE_spec_width = 90
SKYSAT_MS_B4_NIR_spec_width = 160

SKYSAT_MS_spec_centres = c(SKYSAT_MS_B1_B_spec_centre, SKYSAT_MS_B2_R_spec_centre, SKYSAT_MS_B3_RE_spec_centre, SKYSAT_MS_B4_NIR_spec_centre) 

SKYSAT_MS_spec_widths = c(SKYSAT_MS_B1_G_spec_width, SKYSAT_MS_B2_R_spec_width, SKYSAT_MS_B3_RE_spec_width, SKYSAT_MS_B4_NIR_spec_width) 

SKYSAT_MS_spec = data.frame(centre = SKYSAT_MS_spec_centres, width = SKYSAT_MS_spec_widths)

SKYSAT_spec_resp_ffn = "T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/Planet/spectral-response.csv"

SKYSAT_spec_resp = read_csv(SKYSAT_spec_resp_ffn)

SKYSAT_spec_resp$band = factor(SKYSAT_spec_resp$band, levels = c("Blue","Green", "Red", "NIR"))

g = ggplot(SKYSAT_spec_resp) + geom_line(aes(wl*1000, spec_resp, color = band))
g = g + scale_color_manual(values = c("blue","green","red","purple"))
g = g + labs(x = "Wavelength (nm)", y = "Relative spectral response (unitless)", color = "Band")

g

ggsave("T:/Palmerston North/Projects P-T/Remote Sensing of Weeds - Pacific Islands/Data/Rarotonga/Planet/spectral-response.png", g)


```


# CHNK 6007. Develop algorithm to extract these from the HS data

```{r}


#get the bandnumbers and the wavelengths
bnwl = get_bnwl()
bnames_lng = paste0("b", formatC(bnwl$bn, width = 5, flag = "0"), "-", formatC(bnwl$wl, digits = 5))
bnames = paste0("b", formatC(bnwl$bn, width = 3, flag = "0"))


#load an example data set
example_tif_dn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE_EXTR/"
example_tif_fn = "multi_or_TUR_20230811_2BYTE_EXTR_00013_id_tag_00077.tif"
example_tif_ffn = paste0(example_tif_dn, example_tif_fn)

example_img = rast(example_tif_ffn)
example_data = nano_vals(example_img)
example_data_extr = terra::extract(example_img)
example_xy = terra::xyFromCell(example_img,1)

class(example_data)

# the above is difficult try using terraextract(


POLY_fn = "M600-NANO-TUR-230811-80M-POLYLBL-N00007-V01.shp"
POLY_ffn = paste0(align_dn, POLY_fn)
POLY = st_read(POLY_ffn)


r_TUR_HS_80m_ffn = "F:/HAHS_DATA/RARO/FLIGHT_100097_TUR_80m_E_20230811_230225/multi_or/tiles_2BYTE/multi_or_TUR_20230811_2BYTE.kea"
r_TUR_HS_80m = rast(r_TUR_HS_80m_ffn)

# crop and mask

r_ffn = r_TUR_HS_80m_ffn
v_ffn = POLY_ffn
id_tag = "id"
r <- rast(r_ffn)
r_crs = crs(r)
v_unprj <- vect(v_ffn)
v = project(v_unprj,r_crs)
vsel = v[7,] 

r_extr = terra::extract(r, vsel, ID=T, xy=T, cells=T) %>% as_tibble()

r_extr %>% pull(cell) %>% min()
r_extr %>% pull(cell) %>% max()


names(r_extr)
names(r_extr)[2:270] = bnames

r_extr_tr = r_extr %>% select(contains("b")) %>% 
  as.matrix() %>% 
  t %>% 
  as.data.frame %>% 
  as_tibble() %>% 
  bind_cols(bnwl) %>% 
  select(bn, wl, everything())

#grab the MAVIC BBands

band_spec = MAVIC_MS_spec
band_spec = SKYSAT_MS_spec


for (iband in 1:nrow(band_spec)){
  
  cband = band_spec[iband,]
  cband_min = cband$centre - 0.5 * cband$width
  cband_max = cband$centre + 0.5 * cband$width
  
  band_extr = r_extr_tr[r_extr_tr$wl >= cband_min & r_extr_tr$wl <= cband_max,]
  
  band_extr = r_extr_tr %>% filter(wl >= cband_min & wl <= cband_max) %>% 
    summarise(across(everything(), mean)) %>% 
    mutate(
      BandNum = iband,
      BandCentre = cband$centre,
      BandWidth = cband$width
    ) %>% 
    select(BandNum, BandCentre, BandWidth, everything())
  
  if (iband==1){
    
    SIMUL_BANDS = band_extr
    
  }else{
    
    SIMUL_BANDS = bind_rows(SIMUL_BANDS, band_extr)
    
    
  }
  
  
}

SIMUL_BANDS





# EASIER STILL

# lookup bands wl and find which band numbers

# band_spec = SKYSAT_MS_spec
band_spec = MAVIC_MS_spec
band_spec_w_bn = band_spec %>% 
  mutate(bn_min = NA, bn_max = NA)

bnwl = get_bnwl()

for (iband in 1:nrow(band_spec)){
  
  # iband = 4
  print(iband)
  c_cent = band_spec$centre[iband]
  c_wid = band_spec$width[iband]
  wl_min =c_cent- c_wid
  wl_max =c_cent+ c_wid
  bands2include = bnwl %>% filter(wl >= wl_min & wl <= wl_max) %>% pull(bn)
  bn_min = min(bands2include)
  bn_max = max(bands2include)
  band_spec_w_bn$bn_min[iband] = bn_min
  band_spec_w_bn$bn_max[iband] = bn_max
  
  r_sel = mean(r[[bn_min:bn_max]], na.rm=T)
  
  if (iband==1){
    
    r_sim = r_sel
    bnames = "B1"
  }else{
    
    r_sim = c(r_sim, r_sel)
    bnames = c(bnames, paste0("B", iband))
  }
    
  
    
}

names(r_sim) <- bnames


# writeRaster(r_sim, paste0(align_dn, "M600-NANO-TUR-230720-80-SKYSAT_SIM-N00010-V01.tif"), overwrite=T)
writeRaster(r_sim, paste0(align_dn, "M600-NANO-TUR-230720-80-MAVICMS_SIM-N00011-V01.tif"), overwrite=T)


plot(r_sim)

r_sel = r[[5:11]]
r_sel_avg = mean(r_sel)

```






# ===================================
# SECTION 7000 - AERIAL - TRAINING POLYGONS 
# ===================================

Have created a layer called: AERIAL-RGB-TUR-230720-1200m-N00009-V01.shp
This contains 247 Polygons, 151 of which are ATT

# CHNK 7001. Create an ATT Only Polygon layer for training on DeepSeg

```{r}


Aerial_POLYLBL_ffn = paste0(align_dn, "AERIAL-RGB-TUR-230720-1200m-N00009-V01.shp")
Aerial_POLYLBL = st_read(Aerial_POLYLBL_ffn)

# filter these for ATT
Aerial_POLYLBL_ATT_only = Aerial_POLYLBL %>% 
  filter(SPS == "ATT")

Aerial_POLYLBL_ATT_only_ffn = paste0(align_dn, "AERIAL-RGB-TUR-230720-1200m-N00009-V01-ATT-ONLY.shp")

st_write(Aerial_POLYLBL_ATT_only, Aerial_POLYLBL_ATT_only_ffn, append=F)






```




# ===================================
# SECTION 8000 - MS ANALYSIS
# ===================================


```{r}









```

